Measuring causal influence with\\ back-to-back regression: the linear case - supplementary material

### 2019-09-25 paper/synthetic.tex
wip
added plots

To simulate a wide range of experimental conditions, we vary $d_x, d_y \in \{ 10, 15, 25, 39, 63, 100 \}$, $n_c \in \{ 1, 2, 6, 15, 39, 100 \}$,
$\text{snr} \in \{ 0.001, 0.015, 0.25, 3.98, 63, 1000 \}$. We discard the cases where $n_c > d_x$. We limit $d_x, d_y$ to 100 in order to keep the running time under 2 hours for each condition.
%

Each condition is simulated under $5$ different random seeds.

@@

We report AUC results in Figure~\ref{fig:auc_plots}, and compare favorably to all baselines.

\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{figures/AUC.png}
  \caption{We show boxplots for the AUC metric obtained in our synthetic experiments. Higher is better. B2B compares favorably to baselines.}
  \label{fig:auc_plots}
\end{figure}

@@

    \For{$i = 1, \ldots, d_x$}{ $K = Id$\; $K[i] \leftarrow 0$\; $H_k =
\text{LinearRegression}(X_{train} K, Y_{train} G_i)$\; $R_{k} =
\text{corr}(X_{test} H_k, Y_{test} G_i)$\; $\Delta R_i = R_{full} - R_{k}$\; }
\Return{$\Delta R$} \caption{B2B feature importance.} \label{algorithm:cdp_fi}
\end{algorithm}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\linewidth]{figures/delta_b2b.png}
  \caption{Boxplots "boxen" of feature importance values relative to B2B on synthetic experiments. Boxes below the dashed line mean B2B is better.}
  \label{}
\end{figure}

>>>>

To simulate a wide range of experimental conditions, we sample 10 values in log-space for $d_x, d_y \in \left[ 10, 100 \right]$, $n_c \in \left[ 3, 63 \right]$,
$\text{snr} \in \left[ 0.001, 10 \right]$. We discard the cases where $n_c > d_x$, limit $d_x, d_y$ to 100 to keep the running time under 2 hours for each condition, and average over 5 random seeds.
%
% Each condition is simulated under $5$ different random seeds.

@@

We report AUC results in Figures~\ref{fig:auc_plots}~(left) and ~\ref{fig:percondition}~(top), and compare favorably to all baselines.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/AUC_R.png}
  \vspace{-4ex}
  \caption{Synthetic experiments. Distribution of differences in AUC (left) and Feature Importance (right) metrics between our method and the baselines. Mass under the dashed line corresponds to B2B outperforming the baseline. \label{fig:auc_plots}}
  \vspace{2ex}
  \includegraphics[width=\linewidth]{figures/AUC_conditions.png}
  \includegraphics[width=\linewidth]{figures/R_conditions.png}
  \vspace{-4ex}
  \caption{Synthetic experiments. Average AUC (top) and Feature Importance R (bottom) metrics as a function of experimental conditions. Higher is better. \label{fig:percondition}}
\end{figure}

\begin{figure}
  \centering
  \label{}
\end{figure}

@@

    \For{$i = 1, \ldots, d_x$}{ $K = Id$\; $K[i] \leftarrow 0$\; $H_k =
\text{LinearRegression}(X_{train} K, Y_{train} G_i)$\; $R_{k} =
\text{corr}(X_{test} H_k, Y_{test} G_i)$\; $\Delta R_i = R_{full} - R_{k}$\; }
\Return{$\Delta R$} \caption{B2B feature importance.} \label{algorithm:b2b_fi}
\end{algorithm}

@@
